Pipit on the Post: Proving Pre- and Post-conditions of Reactive Systems

### 2024-03-21 2024pipit/section/50-Extraction.tex
copy
todos

@@

@@

>>>>

\TODO{include example of translated executable transition system}

@@

\begin{theorem}[execution-equivalence]
  For a well-typed causal expression $e$ and streaming history $\Sigma$, $e$ evaluates to stream $V$ $(\bigsteps{\Sigma}{e}{V})$ if-and-only-if repeated application of the transition system's step on $\Sigma$ also results in $V$.
\end{theorem}

@@

\subsection{Generated C code}
\TODO{describe the structure of the generated C code, and highlight how it can be executed in a real-time (streaming) environment}
